Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-18 src/ms.tex
adding harmonic figure

@@

\begin{deluxetable*}{lllll}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Results of constant Rossby model fits.\label{tab:mcmc}}
\tablehead{
\colhead{Sample} & 
\colhead{\teff range} & 
\colhead{Ro} & 
\colhead{f} & 
\colhead{$T_\mathrm{sys}$ (K)} 
}
\startdata
\textit{Short-period pile-up} \\
\hline
\lamostmcq 10th \prot pctl. & 4500~K--5800~K & 0.37 $\pm$ 0.02 & 0.011 $\pm$ 0.009 &  46 $\pm$ 80 \\
\hline 
\textit{Long-period pile-up} \\
\hline
\lamostmcq 90th \prot pctl. & 5000~K--6250~K & 1.38 $\pm$ 0.04 & 0.011 $\pm$ 0.008 & 49 $\pm$ 19 \\
\lamostmcq 90th \prot pctl. & 5800~K--6250~K & 1.4 $\pm$ 0.1 & 0.019 $\pm$ 0.015 & 44 $\pm$ 43 \\
CKS (CKS \teff) & 5800~K--6250~K & 1.77 $\pm$ 0.07 & 0.02 $\pm$ 0.01 & -70 $\pm$ 15 \\ 
CKS (SPOCS \teff) & 5800~K--6250~K & 1.9 $\pm$ 0.1 & 0.12 $\pm$ 0.01 & -136 $\pm$ 23 \\
CKS (M19 \teff) & 5800~K--6250~K & 1.6 $\pm$ 0.2 & 0.18 $\pm$ 0.02 & 21 $\pm$ 42 \\
\citet{Hall2021} main-sequence & 5000~K--6250~K & 1.7 $\pm$ 0.2 & 0.30 $\pm$ 0.04 & -5 $\pm$ 64 \\
\citet{Hall2021} main-sequence & 5800~K--6250~K & 1.9 $\pm$ 0.4 & 0.27 $\pm$ 0.05 & -29 $\pm$ 79 \\
%All samples & 5000~K--6250~K & 1.47 $\pm$ 0.05 & 0.132 $\pm$ 0.008 & 2 $\pm$ 23 (LAMOST) \\
% & & & & 10 $\pm$ 15 (CKS) \\
% & & & & 61 $\pm$ 21  (Hall) \\
%All samples & 5800~K--6250~K & 1.67 $\pm$ 0.08 & 0.116 $\pm$ 0.009 & -42 $\pm$ 24 (LAMOST) \\
%&  &  &  & -44 $\pm$ 20 (CKS) \\
%&  &  &  & 3 $\pm$ 23 (Hall) \\ 
\enddata
%\tablecomments{}
\end{deluxetable*}

@@

>>>>

\subsection{Detection biases}
\edit1{To this point, we have not addressed the detection biases inherent to Kepler rotation period catalogs. As rotation periods become longer, it becomes more difficult to measure periods directly from rotational brightness modulations in Kepler time series. This is true for at least three reasons: (1) the Kepler baseline is finite, (2) photometric variation amplitude declines with increasing rotation period, and (3) photometric variations tend to become less periodic with increasing rotation period.
\citet{vanSaders2019} addressed this issue in detail...}

@@

\begin{deluxetable*}{lllll}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Results of constant Rossby model fits.\label{tab:mcmc}}
\tablehead{
\colhead{Sample} & 
\colhead{\teff range} & 
\colhead{Ro} & 
\colhead{f} & 
\colhead{$T_\mathrm{sys}$ (K)} 
}
\startdata
\textit{Short-period pile-up} \\
\hline
\lamostmcq 10th \prot pctl. & 4500~K--5800~K & 0.37 $\pm$ 0.02 & 0.011 $\pm$ 0.009 &  46 $\pm$ 80 \\
\hline 
\textit{Long-period pile-up} \\
\hline
\lamostmcq 90th \prot pctl. & 5000~K--6250~K & 1.38 $\pm$ 0.04 & 0.011 $\pm$ 0.008 & 49 $\pm$ 19 \\
\lamostmcq 90th \prot pctl. & 5800~K--6250~K & 1.4 $\pm$ 0.1 & 0.019 $\pm$ 0.015 & 44 $\pm$ 43 \\
CKS (CKS \teff) & 5800~K--6250~K & 1.77 $\pm$ 0.07 & 0.02 $\pm$ 0.01 & -70 $\pm$ 15 \\ 
CKS (SPOCS \teff) & 5800~K--6250~K & 1.9 $\pm$ 0.1 & 0.12 $\pm$ 0.01 & -136 $\pm$ 23 \\
CKS (M19 \teff) & 5800~K--6250~K & 1.6 $\pm$ 0.2 & 0.18 $\pm$ 0.02 & 21 $\pm$ 42 \\
\citet{Hall2021} main-sequence & 5000~K--6250~K & 1.7 $\pm$ 0.2 & 0.30 $\pm$ 0.04 & -5 $\pm$ 64 \\
\citet{Hall2021} main-sequence & 5800~K--6250~K & 1.9 $\pm$ 0.4 & 0.27 $\pm$ 0.05 & -29 $\pm$ 79 \\
\enddata
%\tablecomments{}
\end{deluxetable*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{./figures/harmonic.pdf}
    \caption{}
    \label{fig:harmonic}    
\end{figure}
